Computing astrophysical inferences with diffusive nested sampling

### 2014-03-19 ms.tex
Acknowledgements
paragraph

@@

\begin{theacknowledgments}
Acknowledgements.
\end{theacknowledgments}

>>>>

Recently we investigated a Bayesian approach for finding objects in ``crowded
fields'', small patches of the sky where many stars are visible in an image.
Each star would appear as a point source in the image, except for the effects
of blurring (caused by either diffraction as the light enters the telescope,
or by atmospheric fluctuations), and the images are also typically noisy.

@@

\begin{theacknowledgments}
It is a pleasure to thank David W. Hogg (NYU), Daniel Foreman-Mackey (NYU),
Fengji Hou (NYU), Anna Pancoast (UCSB), and
John Skilling (MaxEnt Data Consultants) for valuable discussions.
\end{theacknowledgments}
